\mode*

\section{Introduction}

\dots

\subsection{What's the problem?}

\dots

\mode<presentation>{%
  \begin{frame}
    \begin{itemize}
      \item \dots
    \end{itemize}
  \end{frame}
}

\subsection{Why is it a problem?}
% Why is it a problem? Research gap left by other approaches?
% Why is it important, why care?

\dots

\mode<presentation>{%
  \begin{frame}
    \begin{itemize}
      \item \dots
    \end{itemize}
  \end{frame}
}

\subsection{What's the approach?}
% What's the approach? How to solve the problem?

\dots

\mode<presentation>{%
  \begin{frame}
    \begin{itemize}
      \item \dots
    \end{itemize}
  \end{frame}
}

\subsection{What are the findings?}
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

\dots

\mode<presentation>{%
  \begin{frame}
    \begin{itemize}
      \item \dots
    \end{itemize}
  \end{frame}
}


\section{Assessment}

The learning objectives that we want to assess are the following, after 
completion of the course we want the student to be able to
\begin{enumerate}[label={(LO\arabic*)},ref=LO\arabic*]
  \item \LOrelate;
  \item \LOevaluate;
  \item \LOapply;
  \item \LOplan; and
  \item \LOcomm.
\end{enumerate}

You should
\begin{itemize}
  \item write a report, and
  \item make a presentation.
\end{itemize}
These should should contain:
\begin{itemize}
  \item your research questions,
  \item how you answered the questions (methods used), and
  \item why those methods answer the questions properly.
\end{itemize}
This assesses \cref{LOrelate,LOevaluate,LOapply,LOcomm}.

You should also
\begin{itemize}
  \item review someone else's report.
\end{itemize}
This assesses \cref{LOrelate,LOevaluate} and provides a learning opportunity 
for \cref{LOcomm}.

The presentation should also include
\begin{itemize}
  \item what you learned from the feedback of the reviewer,
  \item what you learned from the work you reviewed, and
  \item how you would plan differently next time.
\end{itemize}
This assesses \cref{LOcomm,LOplan}.

