\title{%
  How do you know it's secure?
  Passwords
}
\author{Daniel Bosk\thanks{%
    This material is available under the Creative Commons 
    Attribution-NonCommercial-ShareAlike (CC-BY-NC-SA) 4.0 international 
    license.
    The material was written with some aid from GitHub Copilot.
}}
\institute{%
  KTH EECS
}

\begin{frame}
  \maketitle
\end{frame}

\mode*

\begin{abstract}
  \input{abstract.tex}
\end{abstract}

\clearpage

\begin{frame}
  \frametitle{Three Papers on Passwords}
  \begin{itemize}
    \item \fullcite{OfPasswordsAndPeople}
    \item \fullcite{CanLongPasswordsBeSecureAndUsable}
    \item \fullcite{WhyPhishingWorks}
  \end{itemize}
\end{frame}

\section{Related to TAMOS}

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item What type of scientific inferences were they doing?
    \end{itemize}
  \end{question}

  \begin{question}
    \begin{itemize}
      \item What type of observation and measurement?
        \begin{itemize}
          \item Direct or indirect? Instruments?
          \item Needed theory?
        \end{itemize}
    \end{itemize}
  \end{question}

  \begin{question}
    \begin{itemize}
      \item Operationalization?
        \begin{itemize}
          \item What did they measure and how?
          \item Measurement errors?
        \end{itemize}
    \end{itemize}
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item Did they do hypothesis testing?
    \end{itemize}
  \end{question}

  \begin{question}
    \begin{itemize}
      \item How was their experimental setup? Or was it observational?
        \begin{itemize}
          \item Randomize intervention and control?
          \item Background factors?
          \item Blinding?
          \item Natural experiment?
        \end{itemize}
    \end{itemize}
  \end{question}

  \begin{question}
    \begin{itemize}
      \item Error handling?
        \begin{itemize}
          \item Observer effect?
        \end{itemize}
    \end{itemize}
  \end{question}
\end{frame}

\section{More general}

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item We had \citetitle{OfPasswordsAndPeople}, why do we need 
        \citetitle{CanLongPasswordsBeSecureAndUsable}?
    \end{itemize}
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item What can we say about the validity of these results?
    \end{itemize}
  \end{question}

  \begin{question}
    \begin{itemize}
      \item How well representative are the results?
    \end{itemize}
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item What factors affect how users choose passwords?
        \begin{itemize}
          \item Is it just the password policy?
          \item Can we know from these studies?
          \item We'd need more studies focusing on other factors, then a meta-analysis to see what factors are most important and how they interact.
        \end{itemize}
    \end{itemize}
  \end{question}
\end{frame}

\section{Preoceeding to Models}

\begin{frame}
  \begin{question}
    Did they make use of any models?
  \end{question}
\end{frame}

\begin{frame}
  \begin{example}
    \begin{itemize}
      \item Entropy as a model for password strength (guessability).
        \begin{itemize}
          \item However, later works show that it's not that good a model.
        \end{itemize}
    \end{itemize}
  \end{example}

  \begin{remark}
    \begin{itemize}
      \item This is the topic of the next section of the course.
    \end{itemize}
  \end{remark}
\end{frame}

