\title{%
  Scientificity in Security
}
\author{Daniel Bosk\thanks{%
    This material is available under the Creative Commons 
    Attribution-NonCommercial-ShareAlike (CC-BY-NC-SA) 4.0 international 
    license.
    GitHub Copilot was used to autocomplete parts of the source code for this 
    document.
}}
\institute{%
  KTH EECS
}

\begin{frame}
  \maketitle
\end{frame}

\mode*

\begin{abstract}
  \input{abstract.tex}
\end{abstract}

\clearpage


\section{How to design computer security experiments}

\Textcite{HowToDesignComputerSecurityExperiments} gives a good overview of how 
to design computer security experiments.
\begin{frame}
  \begin{question}
    But is that applicable in all parts of security research?
  \end{question}
\end{frame}

\section{Dos and don'ts of machine learning in security}

\Textcite{DosAndDontsML} discusses how to and how not to use machine learning 
in security.

\begin{frame}
  \begin{question}
    Based on this paper, what can we say about the use of machine learning in 
    the website fingerprinting papers?
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    What can we actually say from these results, based on their method?
  \end{question}
\end{frame}

\section{Security as a scientific pursuit}

\Textcite{SoKScienceOfSecurity} discusses security as a scientific pursuit.

\begin{frame}
  \begin{question}
    How did they know that this is so?
    What can we actually say from these results?
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    What assurances can empirical experiments give about security?
  \end{question}

  \begin{question}
    What assurances can deductive reasoning give about security?
  \end{question}
\end{frame}

